Reducing Wasted Evaluations in Cartesian Genetic Programming

### 2013-05-07 Reducing Wasted Evaluations in CGP/main.tex
Updated gitignore, added "make double" functionality
Added non anonymous version of my paper, fixed Bill's author information
Escaped a bunch of stuff in the bib file, added BGGB journal, fixed citation style

\documentclass[runningheads,a4paper]{llncs}

\usepackage{amssymb}
\setcounter{tocdepth}{3}
\usepackage{graphicx}
\usepackage{verbatim}
\usepackage{url}
\usepackage{hhline}
\newcommand{\includegraphicsfit}[1]
{\includegraphics[width=.9\textwidth,height=\textheight,keepaspectratio]{#1}}
%\urldef{\mailsa}\path|{alfred.hofmann, ursula.barth, ingrid.haas, frank.holzwarth,|
%\urldef{\mailsb}\path|anna.kramer, leonie.kunz, christine.reiss, nicole.sator,|
%\urldef{\mailsc}\path|erika.siebert-cole, peter.strasser, lncs}@springer.com|    
\newcommand{\keywords}[1]{\par\addvspace\baselineskip
\noindent\keywordname\enspace\ignorespaces#1}

@@

% the name(s) of the author(s) follow(s) next
%
% NB: Chinese authors should write their first names(s) in front of
% their surnames. This ensures that the names appear correctly in
% the running heads and the author index.
%
\author{Brian W.~Goldman\and William Punch}
%\author{Anonymous Author\and Anonymous Author}
%
%\authorrunning{Lecture Notes in Computer Science: Authors' Instructions}
% (feature abused for this document to repeat the title also on left hand pages)

% the affiliations are given next; don't give your e-mail address
% unless you accept that it will be published
\institute{BEACON Center for the Study of Evolution in Action,\\
Michigan State University, U.S.A.\\
brianwgoldman@acm.org, punch@cse.msu.edu}
%\institute{Department\\ Organization\\ Email}

@@

\section{Cartesian Genetic Programming}
\label{sec:cgp}
Cartesian Genetic Programming is a variant of genetic programming in which
individuals encode directed acyclic graphs (DAG).
An in-depth explanation of CGP is provided in~\cite{miller:2011:chapter2}, but for
our purposes the important features are:
\begin{itemize}
  \item DAGs are represented by a collection of nodes and genes specifying output locations.
  \item Nodes contain genes describing both what function they perform
  and how they connect to other nodes.
  \item Offspring are created using mutation.
  \item Offspring replace parents if they are of the same or greater fitness.
\end{itemize}
CGP's encoding method does not require a node
to connect to an output location, which is required for it to
affect the phenotype of the individual.
These unconnected nodes and their genes are commonly called ``inactive''
and the connected nodes and their genes are called ``active.''
As the topology of the DAG is constantly evolving, the number and location of
active nodes can change from parent to child.
There have been numerous studies on the usefulness of inactive nodes~\cite{vassilev2000neutrality,yu:2001:neutrality}
including an argument that it is desirable to have up
to $95\%$ of the genome inactive~\cite{miller:2006:redundancy}.

>>>>

\documentclass[runningheads,a4paper]{llncs}
%\linespread{2.5}
\usepackage{amssymb}
\setcounter{tocdepth}{3}
\usepackage{graphicx}
\usepackage{verbatim}
\usepackage{url}
\usepackage{hhline}
\newcommand{\includegraphicsfit}[1]
{\includegraphics[width=.9\textwidth,height=\textheight,keepaspectratio]{#1}}
%\urldef{\mailsa}\path|{alfred.hofmann, ursula.barth, ingrid.haas, frank.holzwarth,|
%\urldef{\mailsb}\path|anna.kramer, leonie.kunz, christine.reiss, nicole.sator,|
%\urldef{\mailsc}\path|erika.siebert-cole, peter.strasser, lncs}@springer.com|    
\newcommand{\keywords}[1]{\par\addvspace\baselineskip
\noindent\keywordname\enspace\ignorespaces#1}

@@

% the name(s) of the author(s) follow(s) next
%
% NB: Chinese authors should write their first names(s) in front of
% their surnames. This ensures that the names appear correctly in
% the running heads and the author index.
%
\author{Brian W.~Goldman\and William F. Punch}
%\author{Anonymous Author\and Anonymous Author}
%
%\authorrunning{Lecture Notes in Computer Science: Authors' Instructions}
% (feature abused for this document to repeat the title also on left hand pages)

% the affiliations are given next; don't give your e-mail address
% unless you accept that it will be published
\institute{BEACON Center for the Study of Evolution in Action,\\
Michigan State University, U.S.A.\\
brianwgoldman@acm.org, punch@msu.edu}
%\institute{Department\\ Organization\\ Email}

@@

\section{Cartesian Genetic Programming}
\label{sec:cgp}
Cartesian Genetic Programming is a variant of genetic programming in which
individuals encode directed acyclic graphs (DAG).
An in-depth explanation of CGP is provided in~\cite{miller:2011:chapter2}, but for
our purposes the important features are:
\begin{itemize}
  \item DAGs are represented by a collection of nodes and genes specifying output locations.
  \item Nodes contain genes describing both what function they perform
  and how they connect to other nodes.
  \item Offspring are created using mutation.
  \item Offspring replace parents if they are of the same or greater fitness.
\end{itemize}
CGP's encoding method does not require a node
to connect to an output location, which is required for it to
affect the phenotype of the individual.
These unconnected nodes and their genes are commonly called ``inactive''
and the connected nodes and their genes are called ``active.''
As the topology of the DAG is constantly evolving, the number and location of
active nodes can change from parent to child.
There have been numerous studies on the usefulness of inactive nodes~\cite{vassilev:2000:neutrality,yu:2001:neutrality}
including an argument that it is desirable to have up
to $95\%$ of the genome inactive~\cite{miller:2006:redundancy}.
